Hippocampal segmentation with MAGeT

### 2012-11-14 paper.Rnw
Moved a2a figures to using facets for more better prettier.
Also included ADNI and SZ demographic data.

\documentclass{article}
\usepackage[margin=1.5in]{geometry}
\usepackage{algorithm}
\usepackage{color}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{url}

@@

\begin{document}
\SweaveOpts{echo = TRUE, message = FALSE, warning = FALSE, fig.align = 'center', tidy = FALSE, comment = NA, cache = TRUE}

<<loadpackages, results="hide", echo=TRUE, cache=FALSE>>=
library(ggplot2)
library(Hmisc)
library(reshape2)
@

@@

@@

Kappa vs. Number of templates: 
Smoothing line fitted using GAM (generalised additive model) from R with defaults from ggplot2 (formula: y ~ s(x, bs = "cs"))

<<a2a, cache=TRUE, fig = T, echo = F, dev='CairoPDF', warning=F, error=F>>=
multiplot <- function(..., plotlist=NULL, cols) {
    require(grid)

    # Make a list from the ... arguments and plotlist
    plots <- c(list(...), plotlist)

    numPlots = length(plots)

    # Make the panel
    plotCols = cols                          # Number of columns of plots
    plotRows = ceiling(numPlots/plotCols) # Number of rows needed, calculated from # of cols

    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(plotRows, plotCols)))
    vplayout <- function(x, y)
        viewport(layout.pos.row = x, layout.pos.col = y)

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
        curRow = ceiling(i/plotCols)
        curCol = (i-1) %% plotCols + 1
        print(plots[[i]], vp = vplayout(curRow, curCol ))
    }

}

#####################################################
# TRACC
t_naive      = read.csv(file='data/a2a_tracc_naive.csv')
t_data       = read.csv(file='data/a2a_tracc_results_2012_08_30.csv')
t_maj        = subset(t_data, method == 'majvote')
t_xcorr      = subset(t_data, method == 'xcorr')
t_nmi        = subset(t_data, method == 'nmi')
t_mean_naive = mean(t_naive$k)
t_ylimits    = c(0.7,0.85)

t_multiatlas = read.csv(file='data/a2a_tracc_multiatlas_2012_08_14.csv')
t_ma_means   = aggregate( k ~ num_atlases , data=t_multiatlas, mean)
t_maj$k_minus_ma_mean   <- t_maj$k   - t_ma_means[ t_maj$num_atlases - 3, 2 ]
t_xcorr$k_minus_ma_mean <- t_xcorr$k - t_ma_means[ t_xcorr$num_atlases - 3, 2 ]
t_nmi$k_minus_ma_mean   <- t_nmi$k   - t_ma_means[ t_nmi$num_atlases - 3, 2 ]

# Majority Vote
# plots kappa by numbeer of templates used
#geom = c('smooth'), line=1.5, formula=y~poly(x,2), method='lm') + 
t_maj_plot <- qplot(x=num_templates, y=k, data=t_maj, colour=as.factor(num_atlases), 
  geom = c('smooth')) + 
geom_hline(aes(yintercept=t_mean_naive)) + 
geom_hline(aes(yintercept = k, colour = as.factor(num_atlases)), linetype="dotted", 
  data = t_ma_means ) + 
opts(title = "ANIMAL\nMajority vote") +
opts(legend.position = "None") + 
scale_colour_hue(name="Atlases") +
xlab( "Number of Templates" ) + 
ylab( "Kappa" ) + 
coord_cartesian(ylim=t_ylimits)

# X-Corr results with a full suite of templates
# plots kappa by top N templates choosen 
t_xcorr_plot <- qplot(x=top_n, y=k, data=t_xcorr,
colour=as.factor(num_atlases), geom=c('smooth')) + 
geom_hline(aes(yintercept=t_mean_naive))  +
coord_cartesian(ylim=t_ylimits) + 
opts(title = "X-Corr vote") +
opts(legend.position = "None") + 
scale_colour_hue(name="Atlases") +
xlab( "Number of Templates" ) + 
ylab( "Kappa" ) + 
coord_cartesian(ylim=t_ylimits)

# NMI results with a full suite of templates
# plots kappa by top N templates choosen 
t_nmi_plot <- qplot(x=top_n, y=k, data=t_nmi,
colour=as.factor(num_atlases), geom=c('smooth')) +
geom_hline(aes(yintercept=t_mean_naive))  +
opts(title = "NMI vote") + 
opts(legend.position = "None") + 
scale_colour_hue(name="Atlases") +
xlab( "Number of Templates" ) + 
ylab( "Kappa" ) + 
coord_cartesian(ylim=t_ylimits)

#####################################################
# ANTS

a_naive      = read.csv(file='data/a2a_ants_naive_2012_08_30.csv')
a_data       = read.csv(file='data/a2a_ants_results_2012_08_30.csv')
a_maj        = subset(a_data, method == 'majvote')
a_xcorr      = subset(a_data, method == 'xcorr')
a_nmi        = subset(a_data, method == 'nmi')
a_mean_naive = mean(a_naive$k)
a_ylimits    = c(0.7,0.85)

a_multiatlas = read.csv(file='data/a2a_ants_multiatlas_2012_08_14.csv')
a_ma_means   = aggregate( k ~ num_atlases , data=a_multiatlas, mean)
a_maj$k_minus_ma_mean   <- a_maj$k - a_ma_means[ a_maj$num_atlases - 3, 2 ]
a_xcorr$k_minus_ma_mean <- a_xcorr$k - a_ma_means[ a_xcorr$num_atlases - 3, 2 ]
a_nmi$k_minus_ma_mean   <- a_nmi$k   - a_ma_means[ a_nmi$num_atlases - 3, 2 ]

# Majority Vote
# plots kappa by numbeer of templates used

a_maj_plot <- qplot(x=num_templates, y=k, data=a_maj, colour=as.factor(num_atlases), 
  geom=c('smooth')) + 
geom_hline(aes(yintercept=a_mean_naive))  +
coord_cartesian(ylim=a_ylimits) + 
geom_hline(aes(yintercept = k, colour = as.factor(num_atlases)), linetype="dotted", 
  data = a_ma_means ) +
opts(title = "ANTS\nMajority vote")  +
opts(legend.position = "None") + 
scale_colour_hue(name="Atlases") +
xlab( "Number of Templates" ) + 
ylab( "Kappa" )

# X-Corr results with a full suite of templates
# plots kappa by top N templates choosen 
a_xcorr_plot <- qplot(x=top_n, y=k, data=a_xcorr,
colour=as.factor(num_atlases), geom=c('smooth')) + 
geom_hline(aes(yintercept=a_mean_naive))  +
opts(title = "X-Corr vote") +
opts(legend.direction = "horizontal") + 
opts(legend.position = "bottom") + 
coord_cartesian(ylim=a_ylimits)  +
scale_colour_hue(name="Atlases") +
xlab( "Number of Templates" ) + 
ylab( "Kappa" )

# NMI results with a full suite of templates
# plots kappa by top N templates choosen 
a_nmi_plot <- qplot(x=top_n, y=k, data=a_nmi,
colour=as.factor(num_atlases), geom=c('smooth')) +
geom_hline(aes(yintercept=a_mean_naive))  +
opts(title = "NMI vote") + 
opts(legend.position = "None") + 
coord_cartesian(ylim=a_ylimits) +
scale_colour_hue(name="Atlases") +
xlab( "Number of Templates" ) + 
ylab( "Kappa" )

#loess.control(trace.hat = c("approximate"), statistics = c("approximate"), surface = c("interpolate"))
#pdf("a2a_kbytemplates.pdf", width=15, height=15)
multiplot(t_maj_plot  , a_maj_plot  ,
          t_xcorr_plot, a_xcorr_plot, 
          t_nmi_plot  , a_nmi_plot  , cols=2)
#dev.off()

############################################
#  Kappa adjusted by Multi-atlas mean 
a_ylimits    = c(-0.03,0.04)
t_ylimits    = a_ylimits

t_maj_plot <- qplot(x=num_templates, y=k_minus_ma_mean, data=t_maj, colour=as.factor(num_atlases), geom = c('smooth'), se=FALSE) + 
opts(title = "ANIMAL\nMajority vote") + opts(legend.position = "None") + 
xlab( "Number of Templates" ) + ylab( "Kappa - MA means" ) + 
coord_cartesian(ylim=t_ylimits)

t_xcorr_plot <- qplot(x=top_n, y=k_minus_ma_mean, data=t_xcorr, colour=as.factor(num_atlases), geom = c('smooth'), se=FALSE) + 
opts(title = "X-Corr vote") + opts(legend.position = "None") + 
xlab( "Number of Templates" ) + ylab( "Kappa - MA means" ) + 
coord_cartesian(ylim=t_ylimits)

t_nmi_plot <- qplot(x=top_n, y=k_minus_ma_mean, data=t_nmi, colour=as.factor(num_atlases), geom = c('smooth'), se=FALSE) + 
opts(title = "NMI vote") + opts(legend.position = "None") + 
xlab( "Number of Templates" ) + ylab( "Kappa - MA means" ) + 
coord_cartesian(ylim=t_ylimits)

a_maj_plot <- qplot(x=num_templates, y=k_minus_ma_mean, data=a_maj, colour=as.factor(num_atlases), geom = c('smooth'), se=FALSE) + 
opts(title = "ANTS\nMajority vote") + opts(legend.position = "None") + 
xlab( "Number of Templates" ) + ylab( "Kappa - MA means" ) + 
coord_cartesian(ylim=a_ylimits)

a_xcorr_plot <- qplot(x=top_n, y=k_minus_ma_mean, data=a_xcorr, colour=as.factor(num_atlases), geom = c('smooth'), se=FALSE) + 
opts(title = "X-Corr vote") + opts(legend.position = "None") + 
xlab( "Number of Templates" ) + ylab( "Kappa - MA means" ) + 
coord_cartesian(ylim=a_ylimits)

a_nmi_plot <- qplot(x=top_n, y=k_minus_ma_mean, data=a_nmi, colour=as.factor(num_atlases), geom = c('smooth'), se=FALSE) + 
opts(title = "NMI vote") + opts(legend.position = "None") + 
xlab( "Number of Templates" ) + ylab( "Kappa - MA means" ) + 
coord_cartesian(ylim=a_ylimits)

#print(a_nmi_plot)
#pdf("a2a_kminusMAmean.pdf", width=15, height=15)
multiplot(t_maj_plot  , a_maj_plot  ,
          t_xcorr_plot, a_xcorr_plot, 
          t_nmi_plot  , a_nmi_plot  , cols=2)
#dev.off()
@

@@

\begin{table}
    \begin{tabular}{c|c|c}
        Number of Atlases & ANIMAL Kappa (Jaccard) & ANTS Kappa (Jaccard) \\ \hline
        3                 & 0.76 (0.63)             & 0.80 (0.69)          \\ 
        4                 & 0.75 (0.62)             & 0.79 (0.67)          \\ 
        5                 & 0.79 (0.66)             & 0.82 (0.71)          \\ 
        6                 & 0.78 (0.65)             & 0.82 (0.70)          \\ 
        7                 & 0.80 (0.67)             & 0.83 (0.72)          \\ 
        8                 & 0.79 (0.67)             & 0.83 (0.72)          \\ 
        9                 & 0.80 (0.68)             & 0.84 (0.73)          \\
    \end{tabular}
\end{table}

>>>>

\documentclass{article}
\usepackage[margin=1.5in]{geometry}
\usepackage{algorithm, color,algpseudocode, amsmath, url, geometry, ctable }

@@

\begin{document}
\SweaveOpts{echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center', tidy = FALSE, comment = NA, cache = TRUE}

<<loadpackages, results="hide", echo=FALSE, cache=FALSE>>=
library(ggplot2)
library(Hmisc)
library(reshape2)
library(ADNIMERGE)
@

@@

<<ADNI-69-demographics, echo=F, results="asis",cache=FALSE>>=
adni_69_RIDs = c("295","413","619","685","729","782","938","954",
                 "1018","1155","907","981","222","324","448","546",
                 "553","572","602","610","814","1341","675","681",
                 "731","1130","41","68","70","101","249","293","316",
                 "414","698","1206","1222","1339","751","1030","3",
                 "5","10","16","22","53","168","183","241","1205",
                 "328","1095","991","213","159","337","343","642",
                 "753","1109","1217","29","56","1188","1293","149",
                 "382","431","1202")
tab <- summary(DX.bl ~ AGE + PTGENDER + PTEDUCAT + PTMARRY + PTETHCAT + PTRACCAT + CDRSB + ADAS13 + MMSE, 
               data = adnimerge, subset = VISCODE == 'bl' & RID %in% adni_69_RIDs, 
               method = "reverse", test=TRUE, overall=TRUE)

latex(tab, file="", size="scriptsize", where="h",landscape=TRUE, ctable=TRUE)
@

@@

Kappa vs. Number of templates: 
Smoothing line fitted using GAM (generalised additive model) from R with defaults from ggplot2 (formula: y ~ s(x, bs = "cs"))
<<a2a_facet, cache=TRUE, fig=TRUE>>=
t_data       = read.csv(file='data/a2a_tracc_results_2012_08_30.csv')
a_data       = read.csv(file='data/a2a_ants_results_2012_08_30.csv')

t_multiatlas = read.csv(file='data/a2a_tracc_multiatlas_2012_08_14.csv')
a_multiatlas = read.csv(file='data/a2a_ants_multiatlas_2012_08_14.csv')
t_ma_means   = aggregate( k ~ num_atlases , data=t_multiatlas, mean)
a_ma_means   = aggregate( k ~ num_atlases , data=a_multiatlas, mean)

# add registration method to data frames (before joining)
t_data       = cbind(t_data, reg_method = "ANIMAL")
a_data       = cbind(a_data, reg_method = "ANTS")

# add column with kappa - multiatlas mean
# num_atlases - 2 is a cheap trick to perform the necessary lookup into the ma_means tables
t_data$k_minus_ma = t_data$k - t_ma_means[ t_data$num_atlases - 2, 2 ]
a_data$k_minus_ma = a_data$k - a_ma_means[ a_data$num_atlases - 2, 2 ]

all_data     = rbind(t_data,a_data)

# use top_n as the number of templates for weighted voting schemes
all_data[ all_data$method != "majvote", ]$num_templates = all_data[ all_data$method != "majvote", ]$top_n

t_naive      = read.csv(file='data/a2a_tracc_naive.csv')
a_naive      = read.csv(file='data/a2a_ants_naive_2012_08_30.csv')
t_mean_naive = mean(t_naive$k)
a_mean_naive = mean(a_naive$k)
df_naive     = data.frame(
                value = c(rep(t_mean_naive,3),rep(a_mean_naive,3)),
                method = rep(c("majvote", "nmi", "xcorr"),2), 
                reg_method = c(rep("ANIMAL",3),rep("ANTS",3)))

method_labels <- list("Majority Vote" = "majvote", "NMI Vote" = "nmi", "Cross-correlation Vote" = "xcorr")
levels(all_data$method) <- method_labels
levels(df_naive$method) <- method_labels

ggplot(all_data, aes(x=num_templates, y=k, colour=as.factor(num_atlases))) + 
  facet_grid(method ~ reg_method) + 
  geom_smooth() + 
  geom_hline(data = df_naive, aes(yintercept = value, linetype="dashed")) + 
  scale_colour_hue(name="Atlases") +
  xlab( "Number of Templates" ) + ylab( "Mean Kappa" ) 
@

<<a2a_facet_mameans, cache=TRUE, fig=TRUE>>=
ggplot(all_data, aes(x=num_templates, y=k_minus_ma, colour=as.factor(num_atlases))) + 
  facet_grid(method ~ reg_method) + 
  geom_smooth() + 
  scale_colour_hue(name="Atlases") +
  xlab( "Number of Templates" ) + ylab( "Difference in mean Kappa between voting method and multiatlas" )
@

@@

<<a2a_multiatlas_means, results="asis",cache=FALSE>>=
latex(merge(a_ma_means, t_ma_means, by="num_atlases"), colheads=c("Atlases", "ANTS", "ANIMAL"), file="")
@
\begin{table}
    \begin{tabular}{c|c|c}
        Number of Atlases & ANIMAL Kappa (Jaccard) & ANTS Kappa (Jaccard) \\ \hline
        3                 & 0.76 (0.63)             & 0.80 (0.69)          \\ 
        4                 & 0.75 (0.62)             & 0.79 (0.67)          \\ 
        5                 & 0.79 (0.66)             & 0.82 (0.71)          \\ 
        6                 & 0.78 (0.65)             & 0.82 (0.70)          \\ 
        7                 & 0.80 (0.67)             & 0.83 (0.72)          \\ 
        8                 & 0.79 (0.67)             & 0.83 (0.72)          \\ 
        9                 & 0.80 (0.68)             & 0.84 (0.73)          \\
    \end{tabular}
\end{table}

### 2012-11-14 paper.tex
Moved a2a figures to using facets for more better prettier.
Also included ADNI and SZ demographic data.

\usepackage{alltt}
\usepackage[margin=1.5in]{geometry}
\usepackage{algorithm}
\usepackage{color}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{url}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlfunctioncall{library}(ggplot2)
\hlfunctioncall{library}(Hmisc)
\hlfunctioncall{library}(reshape2)
\end{alltt}
\end{kframe}
\end{knitrout}

@@

@@

Kappa vs. Number of templates: 
Smoothing line fitted using GAM (generalised additive model) from R with defaults from ggplot2 (formula: y ~ s(x, bs = "cs"))

@@

{\centering \includegraphics[width=\maxwidth]{figure/a2a1}

{\centering \includegraphics[width=\maxwidth]{figure/a2a2}

@@

>>>>

\usepackage{alltt}
\usepackage[margin=1.5in]{geometry}
\usepackage{algorithm, color,algpseudocode, amsmath, url, geometry, ctable }

@@

@@

% latex.default(cstats, title = title, caption = caption, rowlabel = rowlabel,      col.just = col.just, numeric.dollar = FALSE, insert.bottom = legend,      rowname = lab, dcolumn = dcolumn, extracolheads = extracolheads,      extracolsize = Nsize, ...) 
%
{\scriptsize\ctable[caption={Descriptive Statistics by Baseline Dx},label=tab,rotate]{lccccc}{\tnote[]{\noindent {\scriptsize $a$\ }{$b$\ }{\scriptsize $c$\ } represent the lower quartile $a$, the median $b$, and the upper quartile $c$\ for continuous variables.}\tnote[]{Numbers after percents are frequencies.}\tnote[]{\indent Tests used:}\tnote[]{\textsuperscript{\normalfont 1}Kruskal-Wallis test; \textsuperscript{\normalfont 2}Pearson test}}{\FL
\multicolumn{1}{l}{}&\multicolumn{1}{c}{CN}&\multicolumn{1}{c}{LMCI}&\multicolumn{1}{c}{AD}&\multicolumn{1}{c}{Combined}&\multicolumn{1}{c}{Test Statistic}\NN
&\multicolumn{1}{c}{{\scriptsize $N=23$}}&\multicolumn{1}{c}{{\scriptsize $N=23$}}&\multicolumn{1}{c}{{\scriptsize $N=23$}}&\multicolumn{1}{c}{{\scriptsize $N=69$}}&\ML
Age~at~baseline~\hfill\tiny{Years}&{\scriptsize 72.20~}{75.50 }{\scriptsize 78.45} &{\scriptsize 71.00~}{77.10 }{\scriptsize 81.40} &{\scriptsize 71.70~}{77.80 }{\scriptsize 81.75} &{\scriptsize 71.50~}{76.60 }{\scriptsize 81.30} &$ F_{2,66}=0.15 ,~ P=0.862 ^{1} $\NN
Sex~:~Female&43\%~{\scriptsize~(10)}&43\%~{\scriptsize~(10)}&43\%~{\scriptsize~(10)}&43\%~{\scriptsize~(30)}&$ \chi^{2}_{2}=0 ,~ P=1 ^{2} $\NN
Education&{\scriptsize 16.0~}{16.0 }{\scriptsize 18.0} &{\scriptsize 15.0~}{16.0 }{\scriptsize 18.0} &{\scriptsize 12.0~}{16.0 }{\scriptsize 16.5} &{\scriptsize 14.0~}{16.0 }{\scriptsize 18.0} &$ F_{2,66}=3.44 ,~ P=0.038 ^{1} $\NN
Marital~status~at~baseline~:~Married&74\%~{\scriptsize~(17)}&87\%~{\scriptsize~(20)}&87\%~{\scriptsize~(20)}&83\%~{\scriptsize~(57)}&$ \chi^{2}_{4}=3.04 ,~ P=0.551 ^{2} $\NN
~~~~Widowed&22\%~{\scriptsize~(~5)}&13\%~{\scriptsize~(~3)}&13\%~{\scriptsize~(~3)}&16\%~{\scriptsize~(11)}&\NN
~~~~Divorced&~4\%~{\scriptsize~(~1)}&~0\%~{\scriptsize~(~0)}&~0\%~{\scriptsize~(~0)}&~1\%~{\scriptsize~(~1)}&\NN
~~~~Never~married&~0\%~{\scriptsize~(~0)}&~0\%~{\scriptsize~(~0)}&~0\%~{\scriptsize~(~0)}&~0\%~{\scriptsize~(~0)}&\NN
~~~~Unknown&~0\%~{\scriptsize~(~0)}&~0\%~{\scriptsize~(~0)}&~0\%~{\scriptsize~(~0)}&~0\%~{\scriptsize~(~0)}&\NN
Ethnicity~:~Unknown&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&$^{2}$\NN
~~~~Not~Hisp/Latino&100\%~{\scriptsize~(23)}&100\%~{\scriptsize~(23)}&100\%~{\scriptsize~(23)}&100\%~{\scriptsize~(69)}&\NN
~~~~Hisp/Latino&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&\NN
Race~:~Am~Indian/Alaskan&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&$ \chi^{2}_{2}=5.61 ,~ P=0.061 ^{2} $\NN
~~~~Asian&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&\NN
~~~~Hawaiian/Other~PI&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&\NN
~~~~Black&~17\%~{\scriptsize~(~4)}&~~4\%~{\scriptsize~(~1)}&~~0\%~{\scriptsize~(~0)}&~~7\%~{\scriptsize~(~5)}&\NN
~~~~White&~83\%~{\scriptsize~(19)}&~96\%~{\scriptsize~(22)}&100\%~{\scriptsize~(23)}&~93\%~{\scriptsize~(64)}&\NN
~~~~More~than~one&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&\NN
~~~~Unknown&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&~~0\%~{\scriptsize~(~0)}&\NN
CDR-SB&{\scriptsize 0.00~}{0.00 }{\scriptsize 0.00} &{\scriptsize 0.75~}{1.50 }{\scriptsize 1.50} &{\scriptsize 4.00~}{4.50 }{\scriptsize 5.00} &{\scriptsize 0.00~}{1.50 }{\scriptsize 4.00} &$ F_{2,66}=294.2 ,~ P<0.001 ^{1} $\NN
ADAS~13&{\scriptsize  4.665~}{ 5.670 }{\scriptsize 12.335} &{\scriptsize 14.335~}{16.000 }{\scriptsize 20.500} &{\scriptsize 23.830~}{29.000 }{\scriptsize 31.665} &{\scriptsize 10.000~}{16.000 }{\scriptsize 25.330} &$ F_{2,66}=109.8 ,~ P<0.001 ^{1} $\NN
MMSE&{\scriptsize 28.5~}{29.0 }{\scriptsize 30.0} &{\scriptsize 25.0~}{27.0 }{\scriptsize 28.0} &{\scriptsize 21.0~}{23.0 }{\scriptsize 24.0} &{\scriptsize 24.0~}{27.0 }{\scriptsize 29.0} &$ F_{2,66}=94.17 ,~ P<0.001 ^{1} $\LL
}}

@@

Kappa vs. Number of templates: 
Smoothing line fitted using GAM (generalised additive model) from R with defaults from ggplot2 (formula: y ~ s(x, bs = "cs"))
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figure/a2a_facet}

@@

{\centering \includegraphics[width=\maxwidth]{figure/a2a_facet_mameans}

@@

% latex.default(merge(a_ma_means, t_ma_means, by = "num_atlases"),      colheads = c("Atlases", "ANTS", "ANIMAL"), file = "") 
%
\begin{table}[!tbp]
\begin{center}
\begin{tabular}{lrrr}
\hline\hline
\multicolumn{1}{l}{merge}&\multicolumn{1}{c}{Atlases}&\multicolumn{1}{c}{ANTS}&\multicolumn{1}{c}{ANIMAL}\tabularnewline
\hline
1&$3$&$0.805414417498623$&$0.764266832660852$\tabularnewline
2&$4$&$0.793646605043623$&$0.752420649183594$\tabularnewline
3&$5$&$0.823292141139203$&$0.785546924392891$\tabularnewline
4&$6$&$0.815578947302174$&$0.778345910844141$\tabularnewline
5&$7$&$0.831936342756014$&$0.797761650124922$\tabularnewline
6&$8$&$0.826298462726884$&$0.792443538092187$\tabularnewline
7&$9$&$0.836877632304638$&$0.804568318173359$\tabularnewline
\hline
\end{tabular}
\end{center}
\end{table}
